Spike Spectra for Recurrences

### 2022-11-16 Manuscript/entropy-1919488  proof/entropy-1919488.tex
update references and textfile with all the changes

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Potsdam Institute for Climate Impact Research, Member of the Leibniz Association, 14473 Potsdam, Germany; \hl{hellmann@pik-potsdam.de (F.H.); anvari@pik-potsdam.de (M.A.); kurths@pik-potsdam.de (J.K.)} %MDPI: We added the email addresses here according to the submitting system. Please confirm.
\\
$^{2}$ \quad Institute of Physics and Astronomy, University of Potsdam, 14476 Potsdam, Germany\\
\hl{$^{3}$} %MDPI: The affiliation numbers should appear in numerical order. Please check the suggested changes.
 \quad Institute of Physics, Humboldt Universit\"at zu Berlin, 12489 Berlin, Germany\\
\hl{$^{4}$} \quad Institute of Geosciences, University of Potsdam, 14476 Potsdam, Germany}

@@

\subsection{R \"ossler System}\label{sec_models_roessler}

@@

 \includegraphics[width=0.93\textwidth]{./figures/A3B}
 \caption{\hl{Same as in} %MDPI: please add explanation for A--I
 Figure~\ref{fig_tau_rr_example_roessler}, but here with 5\% additive Gaussian white noise on each component $x$, $y$ and $z$. The appearance of the inter-spike spectra 
 in (\textbf{J}--\textbf{L}), and the Fourier spectra in (\textbf{M},\textbf{N},\textbf{P}) are unaffected by the additive noise.}
\label{fig_tau_rr_example_roessler_noise}
\end{figure}

@@

\bibitem[Zhang {et~al.}(2022)Zhang, Widmann, and Barreira]{Zhang2022}
\textls[-15]{Zhang, S.; Widmann, D.; Barreira, D.S}.
\newblock {JuliaOptimalTransport/OptimalTransport.jl: v0.3.19}%MDPI: Please provide more information about the type of the article, such as book (please provide the name of the publisher and location of it), online resource (please provide the URL of the website and the date it was accessed (day, month, year)), or journal article (please provide the name of the journal, the year and volume it published, and the page number).
. {2022}.
\newblock
   \hl{Available online:} %MDPI: we replace the correct web link, please confirm
 \url{https://zenodo.org/record/5920148\#.Y3SbbORByUk} \hl{(accessed on)} %MDPI: Please add accessed date.

@@

\bibitem[GB()]{GB}
National Grid, Frequency Data (2014–2018).
\newblock  \hl{Available online}%MDPI: please add the website link.
:  (accessed on 25 July 2022).

>>>>

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Potsdam Institute for Climate Impact Research (PIK), Member of the Leibniz Association, 14473 Potsdam, Germany; \hl{hellmann@pik-potsdam.de (F.H.); anvari@pik-potsdam.de (M.A.); kurths@pik-potsdam.de (J.K.)} %MDPI: We added the email addresses here according to the submitting system. Please confirm.
%Authors: we agree
\\
$^{2}$ \quad Institute of Physics and Astronomy, University of Potsdam, 14476 Potsdam, Germany\\
\hl{$^{3}$} %MDPI: The affiliation numbers should appear in numerical order. Please check the suggested changes. 
%Authors: we agree
 \quad Institute of Physics, Humboldt Universit\"at zu Berlin, 12489 Berlin, Germany\\
\hl{$^{4}$} \quad Institute of Geosciences, University of Potsdam, 14476 Potsdam, Germany}

@@

\subsection{R\"ossler System}\label{sec_models_roessler}

@@

 \includegraphics[width=0.93\textwidth]{./figures/A3B}
 \caption{\hl{Same as in} %MDPI: please add explanation for A--I 
%Authors: We have added explanations for A--I
 Figure~\ref{fig_tau_rr_example_roessler}, but here with 5\% additive Gaussian white noise on each component $x$, $y$ and $z$. 
 (\textbf{A}) Trajectory of the system in a period-2 (parameter $a=0.36$), (\textbf{B})~in a period-3 (parameter $a=0.41$) and 
 (\textbf{C}) in a chaotic regime (parameter $a=0.428$). 
\mbox{ (\textbf{D}--\textbf{F})}~The corresponding RPs, obtained by using a recurrence threshold corresponding to a 10\% global 
 recurrence rate for (\textbf{D},\textbf{E}) and 5\% for (\textbf{F}). 
  (\textbf{G}--\textbf{I}) $\tau$-RRs of the shown RPs, 
  (\textbf{J}--\textbf{L}) the corresponding inter-spike spectra, and
  (\textbf{M},\textbf{N},\textbf{P}) the Fourier power spectra. 
 The appearance of the inter-spike spectra 
 in (\textbf{J}--\textbf{L}), and the Fourier spectra in (\textbf{M},\textbf{N},\textbf{P}) are unaffected by the additive noise.}
\label{fig_tau_rr_example_roessler_noise}
\end{figure}

@@

\bibitem[Zhang {et~al.}(2022)Zhang, Widmann, and Barreira]{Zhang2022}
\textls[-15]{Zhang, S.; Widmann, D.; Barreira, D.S}.
\newblock {JuliaOptimalTransport/OptimalTransport.jl: v0.3.19, Zenodo}%MDPI: Please provide more information about the type of the article, such as book (please provide the name of the publisher and location of it), online resource (please provide the URL of the website and the date it was accessed (day, month, year)), or journal article (please provide the name of the journal, the year and volume it published, and the page number). 
%Authors: we confirm that we hold the copyright of this figure %Authors: this is a Zenodo repository, no journal article, but we have added "Zenodo"
. {2022}.
\newblock
   \hl{Available online:} %MDPI: we replace the correct web link, please confirm 
   %Authors: we confirm
 \url{https://zenodo.org/record/5920148\#.Y3SbbORByUk} \hl{(accessed on 16 November 2022)} %MDPI: Please add accessed date. 
 %Authors: added

@@

\bibitem[GB()]{GB}
National Grid, Frequency Data (2014–2018).
\newblock  \hl{Available online}%MDPI: please add the website link. %Authors: we added the link
: 
\url{https://www.nationalgrideso.com/industry-information/balancing-services/frequency-response-services/historic-frequency-data} (accessed on 25 July 2022).
